Quality Definitions of Qualities

### 2019-12-04 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated completeness

\wss{Were there any other definitions of completeness?  You could add the
  definition of completeness from \citet[p.\ 5--6]{IEEE1998}.  This definition
  is for requirements, but maybe there is something we can generalize from the
  definition?  We could also look for definitions outside of software
  development.}

>>>>

\begin{defn}
	An SRS is complete if, and only if, it includes the following elements:
\begin{itemize}
\item All significant requirements, whether relating to functionality,
performance, design constraints, attributes, or external interfaces. In
particular any external requirements imposed by a system specification should be
acknowledged and treated.
\item Definition of the responses of the software to all realizable classes of
input data in all realizable classes of situations. Note that it is important to
specify the responses to both valid and invalid input values.
\item Full labels and references to all figures, tables, and diagrams in the SRS
and definition of all terms and units of measure \citep{IEEE1998}.
	\end{itemize}
\end{defn}
\begin{defn}
The quality of being whole or perfect and having nothing missing.
\citep{CambridgeCompleteness2019}.
\end{defn}

\wss{Were there any other definitions of completeness?  You could add the
	definition of completeness from \citet[p.\ 5--6]{IEEE1998}.  This definition
	is for
	requirements, but maybe there is something we can generalize from the
	definition?  We could also look for definitions outside of software
	development.}
\ad{added IEEE and dictionary}
\ad{\url{https://annals-csis.org/proceedings/2016/pliks/468.pdf} has a method of
measuring completeness and consistency, but I haven't summarized any def from it
yet}
